### 2019-12-03 README.rmd

Development versions can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
Note, however, that this branch has not kept pace with the `master` branch or with recent upgrades on CRAN.

@@

## Acknowledgment

>>>>

The development version can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
Note that, in order to build the vignettes, the imported packages **alluvial**, **ggfittext**, and **ggrepel** must be installed. To skip this step, leave `build_vignettes` unspecified or set it to `FALSE`.

The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
Note, however, that this branch has not kept pace with the `master` branch or with recent upgrades on CRAN.

@@

## Acknowledgments
